Change point analysis

### 2023-10-23 stats/lifespan.Rmd
shortened to 8000 words

# how many changepoints?
ibeast$trend$ncp_median

@@

# pull out all relevant change points
cps <- tibble(
          cp = ibeast$trend$cp[1:ibeast$trend$ncp_median], 
          lowerCrI = ibeast$trend$cpCI[1:ibeast$trend$ncp_median,1], 
          upperCrI = ibeast$trend$cpCI[1:ibeast$trend$ncp_median,2]
       )

>>>>

# how many changepoints?
ibeast$trend$ncp_mode

@@

# pull out all relevant change points
cps <- tibble(
          cp = ibeast$trend$cp[1:ibeast$trend$ncp_mode], 
          lowerCrI = ibeast$trend$cpCI[1:ibeast$trend$ncp_mode,1], 
          upperCrI = ibeast$trend$cpCI[1:ibeast$trend$ncp_mode,2]
       )

### 2023-10-23 stats/supplements_changepoint_parameters.Rmd
shortened to 8000 words

# create imprecision as observed in data and as predicted by cp analysis
est <- tibble(age = x, data = y, model = ibeast$trend$Y)
cps <- ibeast$trend$cp[1:ibeast$trend$ncp_median]

>>>>

# create imprecision as observed in data and as predicted by cp analysis
est <- tibble(age = x, data = y, model = ibeast$trend$Y)
cps <- ibeast$trend$cp[1:ibeast$trend$ncp_mode]
